---
title: "Data607 HW2 V2.0"
author: "Ritesh Lohiya"
date: "February 10, 2018"
output: html_document
---

Choose six recent popular movies.  Ask at least five people that you know (friends, family, classmates, imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5.  Take the results (observations) and store them in a SQL database.  Load the information into an R dataframe.

Data has been loaded to the MYSQL Workbench using the below sql query placed at GitHub "https://github.com/Riteshlohiya/Data607-Week-2-Assignment-Movies/blob/master/movies.sql"

I have prepared 2 tables demo(personal information) and ratings(rating of the movies)

#Read the DB password for from the file
```{r}
password = read.table("C:/ProgramData/MySQL/MySQL Server 5.7/Uploads/flights/pass.txt")
```

#install.packages('RMySQL',type='source')
```{r}
library(RMySQL)
library(DBI)
library(ggplot2)
```

Connection to the MySQL:


```{r}
moviesdb = dbConnect(MySQL(), user='root', password=toString(password[1,1]), dbname='movies', host='localhost')
```

List the fields in demo table:

```{r}
dbListFields(moviesdb, 'demo')
```

List the fields in ratings table:

```{r}
dbListFields(moviesdb, 'ratings')
```

Now getting the frequency of the ratings:

```{r}
freq_df<-dbGetQuery(moviesdb,'select movie_name, rating, count(rating) as count
from ratings
group by movie_name,rating
order by movie_name, rating;')
```

View the frequency distribution:

```{r}
freq_df
```

Joining the 2 tables and prepare the dataframes:

```{r}
movies_df<-dbGetQuery(moviesdb, 'select 
a.name, 
a.name_id, 
a.state, 
a.age,
b.movie_name,
b.rating
from demo a
left join ratings b
on a.name_id=b.name_id
order by b.rating
;')
```
Contents of the dataframe
```{r}
head(movies_df)
```

To check if there are any missing values for the ratings:

Contents of the dataframe:

```{r}
colSums(is.na(movies_df))
```
So no missing values.

Frequency by table:
```{r}
table(movies_df$movie_name, movies_df$rating)
```

Ritesh's rating view:

```{r}
Ritesh_Rating <- subset(movies_df, name_id == "A1", select = c(movie_name, 
    rating))

ggplot(Ritesh_Rating, aes(x = movie_name, y = rating, fill = movie_name)) + 
    geom_bar(stat = "identity") + ggtitle("Ritesh Reviews") + xlab("Movie_Name") + 
    ylab("Rating") + guides(fill = FALSE) + theme(axis.text.x = element_text(angle = 45, 
    hjust = 1))
```

Average movie scores:

```{r}
avgscore <- aggregate(movies_df$rating ~ movies_df$movie_name, 
    movies_df, mean)
colnames(avgscore) <- c("movie_name", "mean_score")

ggplot(avgscore, aes(x = movie_name, y = mean_score, fill = movie_name)) + 
    geom_bar(stat = "identity") + ggtitle("Average Scores by movie_name") + 
    xlab("Name") + ylab("Mean Score") + guides(fill = FALSE)
```













